Conditional selectivity for triplestores

### 2012-09-17 conditional/trunk/selectivity-basic.tex
use upright font for sel
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@371 43ef1190-90fd-4dd7-a769-d0121f02b80e
note |d| is void:triples
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@372 43ef1190-90fd-4dd7-a769-d0121f02b80e
Subject and object unbound, predicate bound
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@373 43ef1190-90fd-4dd7-a769-d0121f02b80e

\newcommand{\rdfterm}[1]{\texttt{#1}}
\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}
\newcommand{\sel}[1]{\ensuremath{sel\left(#1\right)}}

@@

In the following, we shall have to introduce to more elaborate
notation to make sure we maintain control of bounded and unbounded
terms. We denote a bounded term with a lowercase letter, $s$
for a subject, $p$ for a predicate and $o$ for object, and variables
are denoted by a question mark, $?$. For example, $p =
\rdfterm{rdf:type}$. We also adopt SPLENDIDs convention of denoting
the number of all triples in certain data source $|d|$.

@@

@@

In this case, we can use Eq.~\ref{eq:sel} directly. We again note that
since the the unbound subject will always have selectivity of
unity.
Eq.~\ref{eq:sel} thus reduces to:

>>>>

\newcommand{\rdfterm}[1]{\texttt{#1}}
\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}
\newcommand{\sel}[1]{\ensuremath{\mathrm{sel}\left(#1\right)}}

@@

In the following, we shall have to introduce to more elaborate
notation to make sure we maintain control of bounded and unbounded
terms. We denote a bounded term with a lowercase letter, $s$
for a subject, $p$ for a predicate and $o$ for object, and variables
are denoted by a question mark, $?$. For example, $p =
\rdfterm{rdf:type}$. We also adopt SPLENDIDs convention of denoting
the number of all triples in certain data source $|d|$ (which can also
be found as the \rdfterm{void:triples} of the dataset).

@@

\paragraph{Subject and object unbound, predicate bound}

By using Eq.~\ref{eq:sel} and swapping $S$ and $P$, we have 
\begin{equation}\label{eq:selsuobunpb}
\sel{T_{\{?~p~?\}}} = \sel{O = ? | P = p \cap S = ?} \cdot 
\sel{S = ? | P = p} \cdot
\sel{P = p} . 
\end{equation}
where we recognize Eqs.~\ref{eq:selSvPp}~and~\ref{eq:selPp} as the
last two parts. The first part, $\sel{O = ? | P = p \cap S = ?}$ must
be computed some other way, by employing heuristics or by using more
advanced statistical methods.

@@

From Eq.~\ref{eq:sel} directly. We again note that
since the the unbound subject will always have selectivity of
unity.
Eq.~\ref{eq:sel} thus reduces to:
